SunPy - Python for Solar Physics

### 2014-01-31 authors.tex

\address{
$^1$ Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
School of Mathematics and Statistics, The University of Sheffield, Hicks 
Building, Hounsfield Road, Sheffield, S3 7RH, UK

@@

$^5$ The Catholic University of America, Washington, DC, USA

$^{6}$ University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany

@@

$^{8}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria

@@

$^{10}$ Masaryk University, Faculty of Informatics, Botanicka 68a Brno, Czech Republic

$^{11}$ Humboldt State University, 1 Harpst St, Arcata, CA, USA

$^{12}$ Boston Python User Group, Boston, MA, USA

$^{13}$ Indian Institute of Technology, Bombay, India

@@

$^{15}$ Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
69117, Germany

$^{16}$ Royal Observatory of Belgium, Brussels, Belgium

$^{17}$ Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
Bogotá, D.C., Colombia

>>>>

\address{
$^1$Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
School of Mathematics and Statistics, The University of Sheffield, Hicks 
Building, Hounsfield Road, Sheffield, S3 7RH, UK

@@

$^5$The Catholic University of America, Washington, DC, USA

$^{6}$University of Bremen, Bibliothekstra\ss e 1, 28359 Bremen, Germany

@@

$^{8}$Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria

@@

$^{10}$Masaryk University, Faculty of Informatics, Botanicka 68a Brno, Czech Republic

$^{11}$Humboldt State University, 1 Harpst St, Arcata, CA, USA

$^{12}$Boston Python User Group, Boston, MA, USA

$^{13}$Indian Institute of Technology, Bombay, India

@@

$^{15}$Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg
69117, Germany

$^{16}$Royal Observatory of Belgium, Brussels, Belgium

$^{17}$Observatorio Astron\'omico Nacional Universidad Nacional de Colombia 
Bogotá, D.C., Colombia
